alloscore, ISF 43

### 2023-06-16 ISF_talk/talk.qmd
more isf edits

Suppose the DM also has a *loss function* $l(a,y)$ - e.g., the lost social/political/economic/psychological/moral utility caused by unmet need when $a < y$ beds are allocated and $y$ severe cases occur - this must somehow acknowledge risk attitude heterogeneity among various DM's that a forecast hub might serve

@@

>>>>

Suppose the DM also has a **loss function** $l(a,y)$

 - unmet need when $a < y$ beds are allocated and $y$ severe cases occur

@@

::: notes
social/political/economic/psychological/moral utility

this must somehow acknowledge risk attitude heterogeneity among various DM's that a forecast hub might serve
:::
